A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-06-13 ms.tex
Minor formatting tweaks.

\subsection*{Data Processing Overview}
\label{sec:data_overview}
The spectra reported here are measured by beam-forming ---phasing the visibilities to
the target location and summing over baselines to produce a spectral time series of perceived flux $S_p$,
which is given by the true source flux, $S$, illuminated by the true beam pattern $B$, according to
% XXX would be nice to capture here and below that B, B_M, and S_p are vectors indexed by t.  would
% suggest subscript, except you already have B_M.  Could use B^\prime (and S^\prime) instead...
\begin{equation}
S_p=BS.
\end{equation}
The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time-average is 
weighted by a model of PAPER's primary beam response ($B_M$).  
\begin{align}
S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M} \nonumber \\ 
&= \frac{\sum_t B_M B}{\sum_t B^2_M} S  \nonumber \\
&= g(\delta) S  \label{eq:g}
\end{align}
% XXX where g and \delta are...?  Should connect this nomeclature to J2331-416 language below (i.e. solving for g)
As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.

@@

\subsection{Observations}

@@

This paper presents a set of detailed total flux measurements, providing
an absolute flux calibration for southern hemisphere EoR studies, as well as a
modest set of verification fluxes for other sources suitable for constraining future primary beam studies.
Here we have provided a measurement of Pictor A with enough precision to confirm
a highly linear spectral index between 150 and 600MHz. We then used the same
filtered beam form method to measure the spectra of bright sources with similar
primary beam response.
Although we focus on a narrow declination range in this paper, the techniques we describe
may be applied over any declination range.  Future work will aim to extend this analysis
to other declination ranges, and to tie the flux calibration of these other declination ranges
back to the absolute flux scale we derive here.

The measurements provided
here are the first, calibrated, broad-band spectra to cover the EoR band. Existing EoR band measurements
are accurate to 20\% implying a 40\% uncertainty in the absolute power spectrum
level.  The PAPER Pictor A spectrum is found to be accurate to 
$\sim$3\%, a factor of 7 improvement over previous EoR-band measurements.

@@

A set of  31 additional verification sources were also targeted to provide additional 
characterization of the flux scale as well as an overall assessment of the catalog accuracy.
.  Using a Bayesian analysis we conclude that most of
these are consistent with previous measurements, provide useful new
constraints and support the conclusion that the  Pictor A flux is likely on the correct scale.

Direct measurements of the Pictor A spectrum are key to correctly setting the
flux scale of PAPER, MWA and future EoR experiments like the Hydrogen Epoch of Reionization Array (HERA).
These spectra provide tighter constraints on many of the EoR band fluxes, while
limiting the pernicious affect of primary beam uncertainty.  Future work will use these
fluxes to further  refine the primary beam models of these experiments which is crucial to properly reconstructing
both image and power spectrum flux.

@@

The PAPER project is supported by the National Science Foundation (awards
0804508, 1129258, and 1125558), and a generous grant from the Mt. Cuba
Astronomical Association.

This work makes use of the ``MCMC Hammer" emcee python library \citep[
\url{http://danfm.ca/emcee/}]{ForemanMackey:2012p8684}  and the NASA/IPAC
Extragalactic Database (NED) which is operated by the Jet Propulsion
Laboratory, California Institute of Technology, under contract with the
National Aeronautics and Space Administration.

>>>>

\subsection{Data Processing Overview}
\label{sec:data_overview}
The spectra reported here are measured by beam-forming ---phasing the visibilities to
the target location and summing over baselines to produce a spectral time series of perceived flux $S_p$,
which is given by the true source flux, $S$, illuminated by the true beam pattern $B$, according to
% XXX would be nice to capture here and below that B, B_M, and S_p are vectors indexed by t.  would
% suggest subscript, except you already have B_M.  Could use B^\prime (and S^\prime) instead...
\begin{equation}
S_p=BS.
\end{equation}
The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time-average is 
weighted by a model of PAPER's primary beam response ($B_M$).  
\begin{align}
S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M} \nonumber \\ 
&= \frac{\sum_t B_M B}{\sum_t B^2_M} S  \nonumber \\
&= g(\delta) S  \label{eq:g}
\end{align}
% XXX where g and \delta are...?  Should connect this nomeclature to J2331-416 language below (i.e. solving for g)
As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.

@@

@@

This paper presents a set of total flux measurements at multiple frequencies within
a 100--200-MHz band, providing
an absolute flux calibration for southern hemisphere EoR studies, as well as a
modest set of verification fluxes for other sources suitable for constraining future primary beam studies.
We have provided a measurement of Pictor A with enough precision to confirm
a linear spectral index between 150 and 600MHz. We apply the same
filtered beamforming method to measure the spectra of bright sources with similar
primary beam response.

The measurements provided
here are the first calibrated, broad-band spectra to cover the EoR band. Existing EoR band measurements
are accurate to 20\% implying a 40\% uncertainty in the absolute power spectrum
level.  The PAPER Pictor A spectrum is found to be accurate to 
$\sim$3\%, a factor of 7 improvement over previous EoR-band measurements.

@@

A set of  31 additional verification sources were also targeted to provide additional 
characterization of the flux scale as well as an overall assessment of the catalog accuracy.
Using a Bayesian analysis, we conclude that most of
these are consistent with previous measurements, provide useful new
constraints and support the conclusion that the Pictor A flux is on the correct scale.

Direct measurements of the Pictor A spectrum are key to correctly setting the
flux scale of PAPER, MWA and future EoR experiments like the Hydrogen Epoch of Reionization Array (HERA).
These spectra provide tighter constraints on many of the EoR band fluxes, while
limiting the pernicious affect of primary beam uncertainty.  Future work will use these
fluxes to further refine the primary beam models of these experiments which is crucial to properly reconstructing
both image and power spectrum flux.
Although we have focused on a narrow declination range in this paper, the techniques we describe
may be applied over any declination range.  Future work will also aim to extend this analysis
to other declination ranges, and to tie the flux calibration of these other declination ranges
back to the absolute flux scale we derive here.

@@

The PAPER project is supported by the National Science Foundation (awards
0804508, 1129258, and 1125558), and a generous grant from the Mt. Cuba
Astronomical Association.
This work makes use of the ``MCMC Hammer" emcee python library \citep[
\url{http://danfm.ca/emcee/}]{ForemanMackey:2012p8684}  and the NASA/IPAC
Extragalactic Database (NED) which is operated by the Jet Propulsion
Laboratory, California Institute of Technology, under contract with the
National Aeronautics and Space Administration.
